Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-15 doc/JFLA2022/Slides/Slides.tex
Slides (small changes)

\begin{frame}
  \frametitle{The Ketonen-Solovay machinery\footnote{Rapidly Growing {R}amsey Functions (1981)}}
    \begin{block}{Formalization}

      $$\omega^{\omega^2+1}+1 \rplus{1} \omega^{\omega^2+1}
      \rplus{2} \omega^{\omega^2}\times 3 
      \rplus{3} \omega^{\omega^2}\times 2 +
      \omega ^ {\omega \times 4}, \dots,2,1,0$$

@@

      $$ \omega^{\omega^2+1}+1 \rplus{1,2,3,4,\dots,x} 0$$
    \end{block}

      \begin{block}{Small steps}
        At time $i$, 
           $\alpha \rplus{i} \canonseq{\alpha}{i}$,
        where $\canonseq{\alpha}{\_}$ is the \emph{canonical sequence} of $\alpha$.
        \begin{itemize}
        \item $\canonseq{0}{i}=0$
        \item $\canonseq{\beta+1}{i}=\beta$
        \item If $\lambda$ is a limit ordinal, then $\lambda$ is the $\omega$-limit of $\canonseq{\lambda}{\_}$.
        \end{itemize}
    \end{block}

@@

\begin{frame}[fragile]
  \begin{block}{Examples}

    \begin{align*}
      H'_{\omega^3}(k) \geq\, & \textit{hyper\_exp2}(k+1) \\
      H'_{\omega^\omega}(k)=\,& \textbf{let}\,F\;f\;i := f^{(i+1)}(i)\,
                      \textbf{in}\, F^{(k)}(\lambda k.\,2k+1)\,k\\
    \end{align*}
       }%mathcolor
  \end{block}

\begin{block}{Lemmas (after K.\& S.)}
   \begin{itemize} 
    \item \textcolor{mathcolor}{$H'_\alpha$} is strictly monotonous

@@

>>>>

\begin{frame}
  \frametitle{The Ketonen-Solovay machinery\footnote{Rapidly Growing {R}amsey Functions (1981)}}
    \begin{block}{Formalization}
      {\color{mathcolor}
      $$\omega^{\omega^2+1}+1 \rplus{1} \omega^{\omega^2+1}
      \rplus{2} \omega^{\omega^2}\times 3 
      \rplus{3} \omega^{\omega^2}\times 2 +
      \omega ^ {\omega \times 4}, \dots,2,1,0$$

@@

      $$ \omega^{\omega^2+1}+1 \rplus{1,2,3,4,\dots,x} 0$$}
    \end{block}

      \begin{block}{Small steps}
        At the $i$-th round, 
           \textcolor{mathcolor}{$\alpha \rplus{i} \canonseq{\alpha}{i}$},
           where \textcolor{mathcolor}{$\canonseq{\alpha}{\_}$} is the \emph{canonical sequence} of \textcolor{mathcolor}{$\alpha$}.

             \begin{itemize}
             \item  \textcolor{mathcolor}{$\canonseq{0}{i}=0$}
             \item \textcolor{mathcolor}{$\canonseq{\beta+1}{i}=\beta$}
             \item If \textcolor{mathcolor}{$\alpha$} is a limit ordinal, then \textcolor{mathcolor}{$\alpha$} is the limit of the sequence
               \textcolor{mathcolor}{$\canonseq{\alpha}{i}_{ (i\in\mathbb{N})}$}.
             \end{itemize}
           \end{block}

@@

\begin{frame}[fragile]

\begin{block}{Lemmas (after K.\,\&\,S.)}
   \begin{itemize} 
    \item \textcolor{mathcolor}{$H'_\alpha$} is strictly monotonous

@@

 \begin{block}{Examples}

        \begin{align*}
        H'_{\omega^\omega}(k)=\,& \textbf{let}\,F\;f\;i := f^{(i+1)}(i)\,
                                  \textbf{in}\, F^{(k)}(\lambda k.\,2k+1)\,k\\
      H'_{\omega^3}(k) \geq\, & \textit{hyper\_exp2}(k+1) \\
      H'_{\omega^\alpha}(k)\geq\,& F_\alpha(k)\; (k>0)\\
    \end{align*}
       }%mathcolor
  \end{block}
